---
title: "Logistic Regression"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise: logistic regression

Using the NH11 data set:

1. Use glm to conduct a logistic regression to predict ever worked (everwrk) using age (age_p) and marital status (r_maritl).

2. Predict the probability of working for each level of marital status.

Note that the data is not perfectly clean and ready to be modeled. You will need to clean up at least some of the variables before fitting the model.

### Part One

Load data, create a new data frame only with variables of interest, examine the data
```{r}
NH11 <- readRDS("NatHealth2011.rds")
NH11.subset <- NH11[c("everwrk", "age_p", "r_maritl")]
summary(NH11.subset)
```


The everwrk variable has many NA's, and other values besides Yes and No.

Create a 'training' data set to build our model by removing all other values besides Yes and No.
Remove unused factors to prevent errors in modelling.
```{r}
train <- subset(NH11.subset, everwrk == "1 Yes" | everwrk == "2 No")
train$everwrk <- factor(train$everwrk)
train$r_maritl <- factor(train$r_maritl)
summary(train)
```


Use glm to conduct a logistic regression to predict ever worked (everwrk) using age (age_p) and marital status (r_maritl)
```{r}
trainLog <- glm(everwrk ~ age_p + r_maritl, data = train, family = binomial)
summary(trainLog)
```

Age, Widowed, Divorced, Never Married and Living with Partner are all statistically significant predictors of ever worked. However, only Widowed and Never Married show a postive correlation.



###Part Two

Predict the probability of working for each level of marital status.

Create a dataset with predictors set at each level of marital status, predict probability of working at each level.
```{r}
predictData <- with(train, expand.grid(r_maritl = levels(train$r_maritl), age_p = mean(age_p)))

cbind(predictData, predict(trainLog, type = "response", se.fit = TRUE, interval = "confidence",
                           newdata = predictData))
```


Based on this model, the probability of working for each level of marital status ranges between 7.2 % and 19.4%
